### 2019-05-25 reports/thesis/chapters/5_inference.tex

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$}
      \end{subfigure}
    }
  \caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
  \label{fig:inference_sep16120deg_zfiltered}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_sep16120deg_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius2_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius2.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_sep16120deg_inference_radius2}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius3_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius3.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_sep16120deg_inference_radius3}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSep16120deg_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius4.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_sep16120deg_inference_radius4}
\end{figure}

The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter. Figure \ref{fig:inference_sep16120deg_zfiltered} shows the filtered $z$ images for various kernel radiuses. For $r=\addNumber{../figures/inference/DefectDetectSep16120deg_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null. When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged. Figures \ref{fig:inference_sep16120deg_inference_radius1} to \ref{fig:inference_sep16120deg_inference_radius4} shows the resulting inference along with the empirical null parameters. The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter. All of the defects were successfully highlighted by the hypothesis test.

@@

The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. Most of false positives around the corners and edges have been eliminated.

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroisep16120deg_inference_radius4}
\end{figure}

>>>>

\begin{figure}[htp]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_z.eps}
        \caption{$r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$}
      \end{subfigure}
    }
  \caption{Filtered $z$ image from the \texttt{Sep16 120deg} dataset. Various kernel radiuses were used.}
  \label{fig:inference_AbsFilterDeg120_zfiltered}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius2_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius2.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius2}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius3_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius3.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius3}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter with radius $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

The empirical null filter was applied to the \texttt{Sep16 120deg} image as shown at the start of the chapter. Figure \ref{fig:inference_AbsFilterDeg120_zfiltered} shows the filtered $z$ images for various kernel radiuses. For $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}$, the resulting $z$ image was smooth and treated everything as the null. When a large enough radius was used, the defects were highlighted by the higher test statistics and everything else remain unchanged. Figures \ref{fig:inference_AbsFilterDeg120_inference_radius1} to \ref{fig:inference_AbsFilterDeg120_inference_radius4} shows the resulting inference along with the empirical null parameters. The figures shows that for large enough kernel radius, the filter ironed out the false positives observed at the start of the chapter. All of the defects were successfully highlighted by the hypothesis test.

@@

The false positives were tackled by manually segmenting the image further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. By using this method, the resulting inference is shown in Figure \ref{fig:inference_subroiAbsFilterDeg120_inference_radius4}. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. Most of false positives around the corners and edges have been eliminated.

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}$. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}
